Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-11-08 R0V0.tex
Added condition to upload to arXiv

@@

\usepackage{hyperref}% backref linktocpage pagebackref
%
\hypersetup{
% Uncomment the line below to remove all links (to references, figures, tables, etc)
%draft, 
colorlinks=true, linktocpage=true, pdfstartpage=1, pdfstartview=FitV,
% Uncomment the line below if you want to have black links (e.g. for printing black and white)
%colorlinks=false, linktocpage=false, pdfborder={0 0 0}, pdfstartpage=3, pdfstartview=FitV, 
breaklinks=true, pdfpagemode=UseNone, pageanchor=true, pdfpagemode=UseOutlines,
plainpages=false, bookmarksnumbered, bookmarksopen=true, bookmarksopenlevel=1,
hypertexnames=true, pdfhighlight=/O, urlcolor=red!50!black, linkcolor=blue!75!black, citecolor=green!50!black,
%
% PDF file meta-information
%
pdftitle={},
pdfauthor={},
pdfsubject={},
pdfkeywords={},
pdfcreator={},
pdfproducer={LaTeX}
}

>>>>

\pdfoutput=1 % to upload to arXiv with the hyperref package

@@

\usepackage[hyperindex,breaklinks]{hyperref}% backref linktocpage pagebackref
%
\hypersetup{
% Uncomment the line below to remove all links (to references, figures, tables, etc)
%draft, 
colorlinks=true, linktocpage=true, pdfstartpage=1, pdfstartview=FitV,
% Uncomment the line below if you want to have black links (e.g. for printing black and white)
%colorlinks=false, linktocpage=false, pdfborder={0 0 0}, pdfstartpage=3, pdfstartview=FitV, 
breaklinks=true, pdfpagemode=UseNone, pageanchor=true, pdfpagemode=UseOutlines,
plainpages=false, bookmarksnumbered, bookmarksopen=true, bookmarksopenlevel=1,
hypertexnames=true, pdfhighlight=/O, urlcolor=red!50!black, linkcolor=green!50!black, citecolor=green!50!black,
%
% PDF file meta-information
%
pdftitle={},
pdfauthor={},
pdfsubject={},
pdfkeywords={},
pdfcreator={},
pdfproducer={LaTeX}
}
